SS finding report

### 2021-12-14 experiments/0_ss_finding/replication_method/3_strains/3_strains.Rmd
lots

```{r}
options(mc.cores = 7)
```

@@

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
#grid_num_a <- 10 ## FOR TEST
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

Bring in various stable state datasets
```{r eval = eval_dynamics_flag}
cluster <- multidplyr::new_cluster(7)
multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

@@

@@

@@

@@

for_join <- tibble(CB_var_gmax_s = CB_vars,
                     SB_var_gmax_s = SB_vars)
CBSBPB_stab_data <- stab_data %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

@@

>>>>

```{r}
options(mc.cores = 12)
```

@@

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
#grid_num_a <- 10 ## FOR TEST
a_Os <- 10^seq(-8, -0, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

saveRDS(parameter, here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))

var_expt_9strains <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS")) 
unique_CBs <- unique(var_expt_9strains$CB_var_gmax_s)[c(1, 5, 10, 15, 20)]
unique_SBs <- unique(var_expt_9strains$SB_var_gmax_s)[c(1, 5, 10, 15, 20)]
var_expt_smaller <- var_expt %>%
  filter(CB_var_gmax_s %in% unique_CBs & SB_var_gmax_s %in% unique_SBs)

saveRDS(var_expt_smaller, here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
system.time(
run_ss_var_experiment(
  parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
  saveRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
)
```

@@

Bring in various stable state datasets
```{r eval = eval_dynamics_flag}
cluster <- multidplyr::new_cluster(12)
multidplyr::cluster_library(cluster, c("microxanox", "dplyr"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/3_strains/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/3_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
```

@@

medium_diversity_varexp_row <- 12

@@

p5  <- plot_ss_result1(var_expt,
                result_index = medium_diversity_varexp_row,
                filename_prefix = NULL,
                save_image_file = FALSE)
p5

@@

p_overlay4 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[medium_diversity_varexp_row,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay4

@@

for_join <- tibble(CB_var_gmax_s = sort(CB_vars),
                     SB_var_gmax_s = sort(SB_vars))
CBSBPB_stab_data <- stab_data %>%
  right_join(for_join) %>%
  mutate(var_treat = "CB-SB-PB",
         var_gmax = CB_var_gmax_s)

@@

# Stable state finding 2

```{r eval = FALSE}
rm(list = ls())
library(here)
library(tidyverse)
library(microxanox)
library(patchwork)
source(here("R/various_useful_functions.r"))

parameter = readRDS(here("experiments/3_strains/data/parameter_1e6_x2x6_factorial.RDS"))
var_expt = readRDS(here("experiments/3_strains/data/var_expt_1e6_x2x6_factorial.RDS"))

var_expt_levels_3s <- var_expt[,1:6]

## here we choose the diversity of the system
wait_time <- 100000
parameter$log10a_series <- log10(sort(unique(parameter$ss_expt$a_O)))
#parameter$log10a_series <- seq(-2.5, -2, 0.025)
parameter$log10a_series <- seq(-8, 0, length = 100)

no_diverity_varexp_row <- 1
no_div_res <- get_ss_temporal_method(parameter, var_expt,
                                     no_diverity_varexp_row,
                                     wait_time)
saveRDS(no_div_res, here("experiments/3_strains/data/no_div_temporal_ss.RDS"))

medium_diverity_varexp_row <- 18
medium_div_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diverity_varexp_row,
                                     wait_time)
saveRDS(medium_div_res, here("experiments/3_strains/data/medium_div_temporal_ss.RDS"))

medium_diversity_onlyCB_varexp_row <- 16
medium_divCB_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diversity_onlyCB_varexp_row,
                                     wait_time)
saveRDS(medium_divCB_res, here("experiments/3_strains/data/medium_divCB_temporal_ss.RDS"))

medium_diversity_onlySBPB_varexp_row <- 3
medium_divSBPB_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diversity_onlySBPB_varexp_row,
                                     wait_time)
saveRDS(medium_divSBPB_res, here("experiments/3_strains/data/medium_divSBPB_temporal_ss.RDS"))

```{r}
no_div_res <- readRDS(here("experiments/3_strains/data/no_div_temporal_ss.RDS"))
medium_div_res <- readRDS(here("experiments/3_strains/data/medium_div_temporal_ss.RDS"))
medium_divCB_res <- readRDS(here("experiments/3_strains/data/medium_divCB_temporal_ss.RDS"))
medium_divSBPB_res <- readRDS(here("experiments/3_strains/data/medium_divSBPB_temporal_ss.RDS"))

plot_ss_result3(no_div_res)
plot_ss_result3(medium_div_res)
plot_ss_result3(medium_divCB_res)
plot_ss_result3(medium_divSBPB_res)

plot_ss_result4(no_div_res$all_res,
                medium_div_res$all_res,
                xlims = c(-8, 0))
plot_ss_result4(no_div_res$all_res,
                medium_divCB_res$all_res,
                xlims = c(-8, 0))
plot_ss_result4(no_div_res$all_res,
                medium_divSBPB_res$all_res,
                xlims = c(-8, 0))

### 2021-12-14 experiments/0_ss_finding/replication_method/6_strains/6_strains.Rmd
lots

---
title: "6 strains"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
plot_ss_results <- FALSE
```

@@

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
#grid_num_a <- 10 ## FOR TEST
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial_small.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial_small.RDS"))
```

@@

>>>>

---
title: "6 strains"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 12)
eval_dynamics_flag <- FALSE
plot_ss_results <- FALSE
```

@@

grid_num_a <- 1000 #usually 1000 ## number of a_0 values
#grid_num_a <- 10 ## FOR TEST
a_Os <- 10^seq(-8, 0, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

saveRDS(parameter, here("experiments/6_strains/data/parameter_1e6_x2x6_factorial.RDS"))

var_expt_9strains <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS")) 
unique_CBs <- unique(var_expt_9strains$CB_var_gmax_s)[c(1, 5, 10, 15, 20)]
unique_SBs <- unique(var_expt_9strains$SB_var_gmax_s)[c(1, 5, 10, 15, 20)]
var_expt_smaller <- var_expt %>%
  filter(CB_var_gmax_s %in% unique_CBs & SB_var_gmax_s %in% unique_SBs)
saveRDS(var_expt_smaller, here("experiments/6_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/6_strains/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/6_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
```

@@

medium_diverity_varexp_row <- 12

### 2021-12-14 experiments/0_ss_finding/replication_method/9_strains/9_strains.Rmd
lots

---
title: "9 strains"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

microxanox_release <- "0.3.0"

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
plot_ss_results <- FALSE
```

@@

medium_diverity_varexp_row <- 311

@@

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))

@@

@@

>>>>

---
title: "9 strains"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

microxanox_release <- "0.3.1"

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.3.0")) {
  stop("microxanox version needs to be at least 0.3.0!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
plot_ss_results <- TRUE
```

@@

medium_diverity_varexp_row <- 290

@@

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
#stab_data <- readRDS(here("experiments/9_strains/data/stab_data_1e6_x2x6_factorial.RDS"))
#stab_data_smaller <- stab_data %>%
#  mutate(num_strains = 9) %>%
#  select(1:6, 11:25)
#saveRDS(stab_data_smaller, here("experiments/9_strains/data/small_stab_1e6_x2x6_factorial.RDS"))

#var_expt$pars

stab_data <- readRDS(here("experiments/9_strains/data/small_stab_data_1e6_x2x6_factorial.RDS"))

@@

p_overlay4 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[medium_diverity_varexp_row,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay4

@@

# Stable state finding 2

```{r eval = FALSE}
rm(list = ls())
library(here)
library(tidyverse)
library(microxanox)
library(patchwork)
source(here("R/various_useful_functions.r"))

parameter <- readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
var_expt <- readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
parameter$ss_expt <- NA
var_expt_levels <- var_expt[,1:6]

wait_time <- 1000
#p$log10a_series <- seq(-2.5, -2, 0.025)
parameter$log10a_series <- seq(-8, 0, length = 10)
parameter$minimum_abundances["CB"] <- 1
parameter$minimum_abundances["SB"] <- 1
parameter$minimum_abundances["PB"] <- 1
parameter$event_interval <- 100
parameter$sim_duration <- wait_time * length(parameter$log10a_series)
parameter$sim_sample_interval <- wait_time
```

```{r eval = FALSE}
## Here a test of one run
no_diverity_varexp_row <- 1
parameter$strain_parameter <- var_expt$pars[[no_diverity_varexp_row]]
parameter <- set_temporal_ssfind_initial_state(parameter,
                                               10^5,
                                               10^5,
                                               10^5)
no_div_res <- run_temporal_ssfind_method(parameter)
no_div_res
```

```{r eval = FALSE}
## here a test of an expt run
var_expt <- var_expt[1:2,]
expt_res <- run_temporal_ssfind_experiment(parameter,
                                           var_expt,
                                           total_initial_abundances = 10^5)
```

```{r}
## test the plotting functions
plot_ss_result3(expt_res, 1)
plot_ss_result3(expt_res, 2)
expt_res$ssfind_result[[1]]

temporal_ss_result <- expt_res
temporal_ss_result$CB_var_gmax_s[[1]]
```

```{r eval = FALSE}
saveRDS(no_div_res, here("experiments/9_strains/data/no_div_temporal_ss.RDS"))

medium_diverity_varexp_row <- 290
medium_div_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diverity_varexp_row,
                                     wait_time)
saveRDS(medium_div_res, here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))

medium_diversity_onlyCB_varexp_row <- 281
medium_divCB_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diversity_onlyCB_varexp_row,
                                     wait_time)
saveRDS(medium_divCB_res, here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))

medium_diversity_onlySBPB_varexp_row <- 10
medium_divSBPB_res <- get_ss_temporal_method(parameter, var_expt,
                                     medium_diversity_onlySBPB_varexp_row,
                                     wait_time)
saveRDS(medium_divSBPB_res, here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))

```{r}
no_div_res <- readRDS(here("experiments/9_strains/data/no_div_temporal_ss.RDS"))
medium_div_res <- readRDS(here("experiments/9_strains/data/medium_div_temporal_ss.RDS"))
medium_divCB_res <- readRDS(here("experiments/9_strains/data/medium_divCB_temporal_ss.RDS"))
medium_divSBPB_res <- readRDS(here("experiments/9_strains/data/medium_divSBPB_temporal_ss.RDS"))

plot_ss_result3(no_div_res)
plot_ss_result3(medium_div_res)
plot_ss_result3(medium_divCB_res)
plot_ss_result3(medium_divSBPB_res)

plot_ss_result4(no_div_res$all_res,
                medium_div_res$all_res,
                xlims = c(-8, 0))
plot_ss_result4(no_div_res$all_res,
                medium_divCB_res$all_res,
                xlims = c(-8, 0))
plot_ss_result4(no_div_res$all_res,
                medium_divSBPB_res$all_res,
                xlims = c(-8, 0))

# testing ssfind_temporal method

```{r eval = FALSE}
rm(list = ls())
library(here)
library(tidyverse)
library(microxanox)
library(patchwork)
source(here("R/various_useful_functions.r"))

parameter = readRDS(here("experiments/9_strains/data/parameter_1e6_x2x6_factorial.RDS"))
var_expt = readRDS(here("experiments/9_strains/data/var_expt_1e6_x2x6_factorial.RDS"))
var_expt_levels <- var_expt[,1:6]

wait_time <- 100000

parameter$log10a_series <- log10(sort(unique(parameter$ss_expt$a_O)))
#p$log10a_series <- seq(-2.5, -2, 0.025)
parameter$log10a_series <- seq(-8, 0, length = 100)

parameter$minimum_abundances["CB"] <- 1
parameter$minimum_abundances["SB"] <- 1
parameter$minimum_abundances["PB"] <- 1
parameter$event_interval <- 100
parameter$sim_duration <- wait_time * length(p$log10a_series)
parameter$sim_sample_interval <- wait_time
parameter$strain_parameter$initial_state <-

#p$strain_parameter <- var_expt$pars[[this_diversity_treatment]]

```{r}
run_temporal_ssfind_method <- function(p)
```

```{r}
run_temporal_ssfind_experiment(parameter, var_expt)
```

### 2021-12-14 experiments/0_ss_finding/temporal_method/report.Rmd
lots

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 13)
plot_ss_result4(ss_9s, 1, 13)

plot_ss_result3(ss_3s, 1)
plot_ss_result3(ss_3s, 13)
plot_ss_result4(ss_3s, 1, 13)

@@

```{r}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_grid(num_strains ~ var_treat, scales = "free_y") +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

>>>>

all_stab <- stab_9s

@@

```{r}
plot_ss_result3(ss_9s, 1)
plot_ss_result3(ss_9s, 15)
plot_ss_result4(ss_9s, 1, 15)

plot_ss_result3(ss_3s, 1)
plot_ss_result3(ss_3s, 15)
plot_ss_result4(ss_3s, 1, 15)

@@

```{r}
all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  #facet_grid(num_strains ~ var_treat, scales = "fixed") +
  facet_wrap( ~ var_treat, nrow = 3, scales = "fixed") +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )
